Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-30 Codes/PrepareResults.rmd

vis_all_points <- rbind(vis_res_pred, vis_true_points)
```

@@

```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}
# === Load Results === #
allML_summary_bySim <- readRDS(here("Shared/Results/for_writing/allML_summary_bySim.rds"))
```

@@

```{r, dependson = "source-results"}
# === Set up === #
res_y_train <-
  allML_summary_bySim %>%
  .[type == "train" & Method %in% c("RF", "BRF", "CNN")]

res_y_test <-
  allML_summary_bySim %>%
  .[type == "test" & Method %in% c("RF", "BRF", "CNN")]

# ==== Summary Table ====#
# --- on training data sets--- #
report_table_y_train <-
  res_y_train %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()

@@

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  summary_res_CNN_RF_BRF %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  # set_table_properties(width = .7, layout = "autofit") %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

@@

```{r}
# === Load the data === #
Simres_low <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_low.rds"))

Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))

Simres_low_high<-
 bind_rows(Simres_low, Simres_high, .id = "Degree") %>%
 .[, Degree := ifelse(Degree==1, "Low", "High")] %>%
 .[, Degree := factor(Degree, levels =c("Low", "High"))]

# === Preparation === #
table_optN_prep_low_high <-
  Simres_low_high %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(Degree, type, Method, Model)] %>%
  dcast(Degree + type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA
  )] %>%
  .[, .(Degree, type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]

# === Summary Table (Testing Data sets) === #
table_optN_prep_low_high <- 
  table_optN_prep_low_high %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable() %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    # blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    # blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(5, 8, 11), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4, 5, 7, 8, 10, 11), width = 0.6) %>%
  width(j = 1, width = 0.8) %>%
  width(j = c(3, 6, 9), width = 0.1)

# /*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_low_high <-
  Simres_low_high %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Degree = "Error Size",
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit() %>%
  width(j = 1, width = 0.8)
```

>>>>

vis_all_points <- rbind(vis_res_pred, vis_true_points)

@@

```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}
# === Load Results === #
allML_summary_bySim <- readRDS(here("Shared/Results/for_writing/allML_summary_bySim.rds"))

# === Set up === #
res_y_train <-
  allML_summary_bySim %>%
  .[type == "train" & Method %in% c("RF", "BRF", "CNN")]

res_y_test <-
  allML_summary_bySim %>%
  .[type == "test" & Method %in% c("RF", "BRF", "CNN")]
```

@@

```{r, dependson = "source-results"}
# ==== Summary Table ====#
# --- on training data sets--- #
report_table_y_train <-
  res_y_train %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()

@@

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  summary_res_CNN_RF_BRF %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  # set_table_properties(width = .7, layout = "autofit") %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
  width(j = 12, width = 0.82) %>%
  width(j = 1, width = 0.5) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

@@

```{r}
# === Load the data === #
Simres_low <- 
  here("Shared/Results/for_writing/allML_summary_bySim_low.rds") %>%
  readRDS()

Simres_high <- 
  here("Shared/Results/for_writing/allML_summary_bySim_high.rds") %>%
  readRDS()

Simres_low_high<-
 bind_rows(Simres_low, Simres_high, .id = "Degree") %>%
 .[, Degree := ifelse(Degree==1, "Low", "High")] %>%
 .[, Degree := factor(Degree, levels =c("Low", "High"))] %>%
 .[type == "test",]

# === Preparation === #
table_optN_prep_low_high <-
  Simres_low_high %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(Degree, Method, Model)] %>%
  dcast(Degree + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
  )] %>%
  .[, .(Degree, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]

# === Summary Table (Testing Data sets) === #
table_optN_low_high <- 
  table_optN_prep_low_high %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable() %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11, 13:14), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  width(j = c(2,5,8,11, 14), width=0.3) %>%
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4, 5, 7, 8, 10, 11, 13, 14), width = 0.6) %>%
  width(j = 1, width = 0.82) %>%
  width(j = 2, width = 0.5) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.1)
```

## Yield Prediction

```{r}
# /*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_low_high <-
  Simres_low_high %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Degree = "Error Size",
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit() %>%
  width(j = 1, width = 0.82) %>%
  align(j = 2, align = "left", part = "body") 
```

```{r, dependson = "source-results"}
# === Preparation === #
prepare_count_tbl_low_high <-
  Simres_low_high %>%
  .[Method %in% c("RF", "BRF", "CNN")] %>%
  dcast(Degree + sim + Model ~ Method, value.var = c("pi_loss", "rmse_y")) %>%
  .[, which_ML_y := case_when(
    rmse_y_BRF < rmse_y_RF & rmse_y_BRF < rmse_y_CNN ~ "BRF",
    rmse_y_RF < rmse_y_BRF & rmse_y_RF < rmse_y_CNN ~ "RF",
    rmse_y_CNN < rmse_y_BRF & rmse_y_CNN < rmse_y_RF ~ "CNN"
  )] %>%
  .[, which_ML_piLoss := case_when(
    pi_loss_BRF < pi_loss_RF & pi_loss_BRF < pi_loss_CNN ~ "BRF",
    pi_loss_RF < pi_loss_BRF & pi_loss_RF < pi_loss_CNN ~ "RF",
    pi_loss_CNN < pi_loss_BRF & pi_loss_CNN < pi_loss_RF ~ "CNN"
  )] %>%
  .[, index_cnst_y_piLoss := ifelse(which_ML_piLoss == which_ML_y, 1, 0)] %>%
  .[, ML_cnst_y_piLoss := ifelse(index_cnst_y_piLoss == 1, which_ML_piLoss, NA)] %>%
  .[, .(
    count_BRF = nrow(.SD[ML_cnst_y_piLoss == "BRF", ]),
    count_RF = nrow(.SD[ML_cnst_y_piLoss == "RF", ]),
    count_CNN = nrow(.SD[ML_cnst_y_piLoss == "CNN", ]),
    count_y_BRF = nrow(.SD[which_ML_y == "BRF", ]),
    count_y_RF = nrow(.SD[which_ML_y == "RF", ]),
    count_y_CNN = nrow(.SD[which_ML_y == "CNN", ]),
    Total = sum(index_cnst_y_piLoss)
  ), by = .(Degree, Model)] %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
  )] %>%
  .[, .(Degree, Model, blank1, count_y_RF, count_RF, blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN, blank4, Total)]

# === Table creation === #
count_tbl_low_high <-
  prepare_count_tbl_low_high %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4:5, 7:8, 10:11), width = 0.6) %>%
  width(j = 1, width = 0.82) %>%
  width(j = 13, width = 0.82) %>%
  width(j = 2, width = 0.5) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.1)

### 2022-03-30 Writing/appendix.rmd

```{r report-table-optN-low, tab.cap = "Table G.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
# table_optN_prep_low_high
```

@@

```{r report-table-optN-low, tab.cap = "Table G.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
# report_table_y_low_high
```

```{r count-tbl-low-high, tab.cap = "Table G.3: Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances of prediction-oriented ML methods on low and high degree of yield disturbance datasets"}
# count_tbl_low_high
```

>>>>

```{r report-table-optN-low, tab.cap = "Table G.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
table_optN_low_high
```

@@

```{r report-table-optN-low, tab.cap = "Table G.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
report_table_y_low_high
```

```{r count-tbl-low-high, tab.cap = "Table G.3: Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances of prediction-oriented ML methods on low and high degree of yield disturbance datasets"}
count_tbl_low_high
```
